Efficient toolkit implementing best practices for principal component analysis of population genetic data

### 2019-10-21 paper-bedpca.tex
save PCA UKBB

@@

@@

>>>>

[REDO]

@@

\subsection{PCA of the UK Biobank}

Principal Components (PC) loadings reported by the UK Biobank clearly show that PC19 to PC40 capture LD structure, which is also the case for PC16 and PC18, although less pronounced (see peaks in figure \ref{fig:UKBB-loadings40}). 
Moreover, our automatic procedure removing long-range LD regions did not converge after 5 iterations, meaning that it kept detecting long-range LD regions at each iteration. Therefore, we were able to capture only 16 PCs that shows population stratification and not LD structure (Figures \ref{fig:UKBB-screeplot}, \ref{fig:UKBB-scores} and \ref{fig:UKBB-loadings}).

\noindent[SHOW INITIAL PC SCORES OF UKBB?]

\noindent[COMPUTE MAHA ON LOADINGS TO SHOW THE PEAKS SUMMARIZED IN ALL 16-18 PCS?]

@@

\begin{figure}[!htpb]
\centerline{\includegraphics[width=0.9\textwidth]{UKBB-loadings1-40.pdf}}
\caption{Principal Component (PC) loadings 1 to 40 reported by the UK Biobank.
\label{fig:UKBB-loadings40}}
\end{figure}

\begin{figure}[!htpb]
\centerline{\includegraphics[width=0.8\textwidth]{UKBB-screeplot.pdf}}
\caption{Scree plot: plot of singular values computed from the UK Biobank.
\label{fig:UKBB-screeplot}}
\end{figure}

\begin{figure}[!htpb]
\centerline{\includegraphics[width=0.9\textwidth]{UKBB-PC1-20.png}}
\caption{Principal Component (PC) scores 1 to 20 computed from the UK Biobank.
\label{fig:UKBB-scores}}
\end{figure}

\begin{figure}[!htpb]
\centerline{\includegraphics[width=0.9\textwidth]{UKBB-loadings.pdf}}
\caption{Principal Component (PC) loadings 1 to 20 computed from the UK Biobank.
\label{fig:UKBB-loadings}}
\end{figure}
